---
title: "Portfolio Analysis"
author: "Mohammed Ali"
date: "November 15, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tseries)
library(xts)
library(tseries)
library(PerformanceAnalytics)
```

## Introduction

A golden rule in investing is to always test the portfolio strategy on historical data, and, once you are trading the strategy, to constantly monitor its performance.

This tutorials aims to:

* learn how to estimate the portfolio weights that optimally balance risk and return,

* combine portfolio theory with the practice in R,

* and to illustrate on real-life examples of equity portfolios and asset allocation problems. 

## Data
The following data sets will be used through the tutorial

```{r get_Data}
# Data for the Apple and Microsoft Stock
aapl <- get.hist.quote(instrument="AAPL",start=as.Date("2005-12-31"),end=Sys.Date(),quote="AdjClose",quiet=T)
msft <- get.hist.quote(instrument="MSFT",start=as.Date("2005-12-31"),end=Sys.Date(),quote="AdjClose",quiet=T)

# Data for S&P 500
sp500 <- get.hist.quote(instrument="^GSPC",start=as.Date("1985-12-31"),end=Sys.Date(),quote="AdjClose",quiet=T,compression="d")

# Data on US Equities and bonds 
eq_prices <- get.hist.quote(instrument="SPY",start=as.Date("2003-12-31"),end=as.Date("2016-06-30"),quote="AdjClose",quiet=T,compression="m")
bond_prices <- get.hist.quote(instrument="AGG",start=as.Date("2003-12-31"),end=as.Date("2016-06-30"),quote="AdjClose",quiet=T,compression="m")
eq_prices <- eq_prices/as.numeric(eq_prices[1])
bond_prices <-  bond_prices/as.numeric(bond_prices[1])

```


## The building blocks
Asset returns and portfolio weights; those are the building blocks of a portfolio return. 

## Analyzing performance
The history of portfolio returns reveals valuable information about how much the investor can expect to gain or lose.

## Performance drivers
In addition to studying portfolio performance based on the observed portfolio return series, it is relevant to find out how individual (expected) returns, volatilities and correlations interact to determine the total portfolio performance.

## Optimizing the portfolio
We have up to now considered the portfolio weights as given. Now, we learn how to determine in R the portfolio weights that are optimal in terms of achieving a target return with minimum variance, while satisfying constraints on the portfolio weights.

## Calculating portfolio weights when component values are given
We can easily compute portfolio weights if we have a given amount of money invested in certain assets. If you want to start investing in a portfolio but we have budget restraints, we can also impose weights yourself. Depending on what these are, we will invest a certain amount of money in each of the assets based on their weight.

```{r calc_wreights}
# Define the vector values
values <- c(4000, 4000, 2000)

# Define the vector weights
weights <- values / sum(values)

# Print the resulting weights
weights
```

There is also One of the most commonly used portfolios in investing is the equally weighted portfolio. This means that you choose to invest an equal amount of capital in each asset.

## The weights of a market capitalization weighted portfolio
In a market capitalization weighted portfolio, the weights are given by the individual assets' market capitalization (or market value), divided by the sum of the market capitalizations of all assets. A typical example is the S&P 500 portfolio invested in the 500 largest companies listed on the US stock exchanges (NYSE, Nasdaq). Note that by dividing by the sum of asset values across all portfolio assets, the portfolio weights sum to unity (one).

```{r market_weights}
# Define marketcaps
marketcaps <- c(5, 8, 9, 20, 25, 100, 100, 500, 700, 2000)
  
# Compute the weights
weights <- marketcaps / sum(marketcaps)
  
# Inspect summary statistics
summary(weights)
  
# Create a barplot of weights
  barplot(weights)
```

## Calculation of portfolio returns
A portfolio return is calculated by taking the sum of simple returns multiplied by the portfolio weights. Remember that simple returns are calculated as the final value minus the initial value, divided by initial value.

```{r porto_Return}
# Vector of initial value of the assets
in_values <- c(1000, 5000, 2000)
  
# Vector of final values of the assets
fin_values <- c(1100, 4500, 3000)

# Weights as the proportion of total value invested in each assets
weights <- in_values/sum(in_values)

# Vector of simple returns of the assets 
returns <- (fin_values - in_values) / in_values
  
# Compute portfolio return using the portfolio return formula
preturns <- sum(weights * returns)
```

Note that the weighted average portfolio return equals the percentage change in the total portfolio value. Remember that portfolio returns are calculated by taking the sum of simple returns, multiplied by the portfolio weights.

## From simple to gross and multi-period returns
The simple return R expresses the percentage change in value of an investment. The corresponding so-called "gross" return is defined as the future value of 1 USD invested in the asset for one period, and is thus equal to `1+R`.

The gross return over two periods is obtained similarly. Let `$R1$` be the return in the first period and `$R2$` the return in the second period. Then the end-value of a 1 USD investment is `(1+$R1$)∗(1+$R2$)`.

The corresponding simple return over those two periods is: `(1+$R1$)∗(1+$R2$)−1`.

Suppose that you have an investment horizon of two periods. In the first period you make a 10% return. But in the second period you take a loss of `5%`.

what is the end value of a 1000 USD investment.

```{r}
(1+.1)*(1-0.05) - 1
```


## The asymmetric impact of gains and losses
It is important to be aware of the fact that a positive and negative return of the same relative magnitude do not compensate each other in terms of terminal wealth. Mathematically, this can be seen from the identity (1+x)∗(1−x)=1−x2, which is less than one. A 50% loss is thus not compensated by a 50% gain. After a loss of 50%, what is the return needed to be at par again? `100%`

After 50% loss you would need to double the amount of money you have remaining to return to your initial investment value.



