---
title: "Portfolio Analysis"
author: "Mohammed Ali"
date: "November 15, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tseries)
library(xts)
library(tseries)
```

## Introduction

A golden rule in investing is to always test the portfolio strategy on historical data, and, once you are trading the strategy, to constantly monitor its performance.

This tutorials aims to:

* learn how to estimate the portfolio weights that optimally balance risk and return,

* combine portfolio theory with the practice in R,

* and to illustrate on real-life examples of equity portfolios and asset allocation problems. 

## Data
The following data sets will be used through the tutorial

```{r get_Data}
# Data for the Apple and Microsoft Stock
aapl <- get.hist.quote(instrument="AAPL",start=as.Date("2005-12-31"),end=Sys.Date(),quote="AdjClose",quiet=T)
msft <- get.hist.quote(instrument="MSFT",start=as.Date("2005-12-31"),end=Sys.Date(),quote="AdjClose",quiet=T)

# Data for S&P 500
sp500 <- get.hist.quote(instrument="^GSPC",start=as.Date("1985-12-31"),end=Sys.Date(),quote="AdjClose",quiet=T,compression="d")

# Data on US Equities and bonds 
eq_prices <- get.hist.quote(instrument="SPY",start=as.Date("2003-12-31"),end=as.Date("2016-06-30"),quote="AdjClose",quiet=T,compression="m")
bond_prices <- get.hist.quote(instrument="AGG",start=as.Date("2003-12-31"),end=as.Date("2016-06-30"),quote="AdjClose",quiet=T,compression="m")
eq_prices <- eq_prices/as.numeric(eq_prices[1])
bond_prices <-  bond_prices/as.numeric(bond_prices[1])

```


## The building blocks
Asset returns and portfolio weights; those are the building blocks of a portfolio return. 

## Analyzing performance
The history of portfolio returns reveals valuable information about how much the investor can expect to gain or lose.

## Performance drivers
In addition to studying portfolio performance based on the observed portfolio return series, it is relevant to find out how individual (expected) returns, volatilities and correlations interact to determine the total portfolio performance.

## Optimizing the portfolio
We have up to now considered the portfolio weights as given. Now, we learn how to determine in R the portfolio weights that are optimal in terms of achieving a target return with minimum variance, while satisfying constraints on the portfolio weights.

## Calculating portfolio weights when component values are given
We can easily compute portfolio weights if we have a given amount of money invested in certain assets. If you want to start investing in a portfolio but we have budget restraints, we can also impose weights yourself. Depending on what these are, we will invest a certain amount of money in each of the assets based on their weight.

```{r calc_wreights}
# Define the vector values
values <- c(4000, 4000, 2000)

# Define the vector weights
weights <- values / sum(values)

# Print the resulting weights
weights
```

There is also One of the most commonly used portfolios in investing is the equally weighted portfolio. This means that you choose to invest an equal amount of capital in each asset.

## The weights of a market capitalization weighted portfolio
In a market capitalization weighted portfolio, the weights are given by the individual assets' market capitalization (or market value), divided by the sum of the market capitalizations of all assets. A typical example is the S&P 500 portfolio invested in the 500 largest companies listed on the US stock exchanges (NYSE, Nasdaq). Note that by dividing by the sum of asset values across all portfolio assets, the portfolio weights sum to unity (one).

```{r market_weights}
# Define marketcaps
marketcaps <- c(5, 8, 9, 20, 25, 100, 100, 500, 700, 2000)
  
# Compute the weights
weights <- marketcaps / sum(marketcaps)
  
# Inspect summary statistics
summary(weights)
  
# Create a barplot of weights
  barplot(weights)
```


